\begin{thebibliography}{1}
\bibitem{ref1} Van Der Veen, Victor, Herbert Bos, and Christian Rossow. {\em Dynamic analysis of android malware.} Internet \& Web Technology Master thesis, VU University Amsterdam (2013).
\bibitem{ref2} Unuchek, Roman. {\em Mobile Malware Evolution 2016 - Securelist.} Securelist.com, 2017, \url{https://securelist.com/mobile-malware-evolution-2016/77681/}.
\bibitem{ref3} Stark, Harold. {\em The Google I/O 2017.} Forbes.Com, 2017, \url{https://www.forbes.com/sites/haroldstark/2017/05/20/if-you-couldnt-attend-the-google-io-2017-read-this/}.
\bibitem{ref4} {\em Google Play Protect.} Android Open Source Project, 2017, \url{https://www.android.com/play-protect/}. 
\bibitem{ref5} {\em Millions Of Android Phones Hit By 'Judy' Malware - BBC News.} BBC News, 2017, \url{http://www.bbc.com/news/technology-40092540}.
\bibitem{ref6} {\em Android Compatibility Program Overview} Android Open Source Project, 2017, \url{https://source.android.com/compatibility/overview}.
\bibitem{ref7} {\em IDC: Smartphone OS Market Share.} Www.Idc.Com, 2017, \url{http://www.idc.com/promo/smartphone-market-share/os}.
\bibitem{ref8} {\em App Stores: Number Of Apps In Leading App Stores 2017.} Statista, 2017, \url{https://www.statista.com/statistics/276623/number-of-apps-available-in-leading-app-stores/}.
\bibitem{ref9} {\em Google Play: Number Of Downloads 2010-2016.} Statista, 2017, \url{https://www.statista.com/statistics/281106/number-of-android-app-downloads-from-google-play/}.
\bibitem{ref10} Neuner, Sebastian, et al. {\em Enter sandbox: Android sandbox comparison.} arXiv preprint arXiv:1410.7749 (2014).
\bibitem{ref11} Unuchek, Roman. {\em Dvmap: The First Android Malware With Code Injection - Securelist.} Securelist.Com, 2017, \url{https://securelist.com/dvmap-the-first-android-malware-with-code-injection/78648/}.
\bibitem{ref12} {\em Androguard.} Github, 2017, \url{https://github.com/androguard/androguard}.
\bibitem{ref13} Brahler, Stefan. {\em Analysis Of The Android Architecture.} 2010.
\bibitem{ref14} David Ehringer. {\em The Dalvik Virtual Machine Architecture.} 2010. 
\bibitem{ref15} {\em Tracedroid 4.4 Repository.} Github, 2017, \url{https://github.com/dda410/Bproject}.
\bibitem{ref16} {\em Android Dashboards.} Android Open Source Project, 2017, \url{https://developer.android.com/about/dashboards/index.html}.
\bibitem{ref17} {\em Android Dashboards.} Android Open Source Project, 2017, \url{https://developer.android.com/about/dashboards/index.html}.
\bibitem{ref18} {\em Establishing A Build Environment.} Android Open Source Project, 2017, \url{https://source.android.com/source/initializing}.
\bibitem{ref19} {\em Downloading The Android Source.} Android Open Source Project, 2017, \url{https://source.android.com/source/downloading}.  
\bibitem{ref20} {\em Android Studio.} Android Open Source Project, 2017, \url{https://developer.android.com/studio/index.html}.
\bibitem{ref21} {\em Command Line Tools Android Studio.} Android Open Source Project, 2017, \url{https://developer.android.com/studio/command-line/index.html}.
\bibitem{ref22} {\em Android Debug Bridge.} Android Open Source Project, 2017, \url{https://developer.android.com/studio/command-line/adb.html}.
\bibitem{ref23} {\em Aptoide.} En.Aptoide.com, 2017, \url{https://en.aptoide.com/}.
\bibitem{ref24} {\em Firefox Android Browser.} Mozilla, 2017, \url{https://www.mozilla.org/en-US/firefox/android/}.
\bibitem{ref25} {\em Free Community-Based Navigation App.} Waze.Com, 2017, \url{https://www.waze.com/}.
\bibitem{ref26} {\em List Of Most Downloaded Android Applications.} En.Wikipedia.Org, 2017, \url{https://en.wikipedia.org/wiki/List_of_most_downloaded_Android_applications}.
\bibitem{ref27} {\em Aptoide Downloads} En.Wikipedia.Org, 2017, \url{https://en.wikipedia.org/wiki/Aptoide}.
\bibitem{ref28} Costamagna, Valerio, and Cong Zheng. {\em ARTDroid: A Virtual-Method Hooking Framework on Android ART Runtime.} IMPS@ ESSoS. 2016. APA
\bibitem{ref29} {\em Android 7 Trace.} Android Open Source Project, 2017, \url{https://android.googlesource.com/platform/art/+/master/runtime/trace.cc}.
\end{thebibliography}
